---
title: "Convert pictures to gif"
author: "Jiaxiang Li"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Sometimes we want to share pictures to others, because there contains the bugs or error information which hard display by `reprex`.
However, post a lot of pictures is not friendly-readable even you can use html tag `<details> ... <summary>`.
Thus, gif may be a better solution. 
I wrap a function to convert screenshots or other pictures into a gif.

```{r}
library(add2blog)
add2blog::
```

1. `path` is the directory the pictures stay and `input_like` is a regular expression string to select all matches in this directory. 
: It more serves the practice tasks. Thus, I design it into regular expression string instead of a boring list of all names of pictures you want to convert.
1. `output_name` specifies the output name you like, by default, `tmp.gif`
1. `size` controls the size of gif, by default, `1000 x 1000`
1. `transfer_time` specifies how long the picture changes into the next, by default, `1`

```{r}

```


path <- file.path('../','picbackup')
input_like <- 'reprex'
output_name <- 'reprex201811061210.gif'
